The evolution of gene expression in the term placenta of viviparous mammals

### 2016-03-28 manuscript/manuscript.Rnw
fill out discussion of core placenta transcriptome

\subsection{Annexin and Fetal Immunotolerance}

\DLA{Finish out this section siting Aarli work and Linke work}

@@

The core placenta transcriptome was also identified, which contains
genes which are involved in maternal-fetal tolerance, such as the
annexins, and genes responsible for cell-cell and cell-matrix
interactions, such as \textit{LGALS1}. These genes were almost
certainly present in the ancestral therian placenta. We hypothesize
that modifications to their expression or function will compromise the
development and organization of the placenta.

>>>>

\subsection{Core placenta transcriptome}

The transcriptomes from multiple different species enabled us to
identify the set of expressed genes which are common to all placentas.
Components of the annexin complexes, including including
\textit{ANXA2}, \textit{ANXA1}, \textit{S100A11}, and \textit{S100A10}
are expressed in all placentas examined, and argue for the evolution
importance of annexins in placenta function, where they likely
establish maternal-fetal
tolerance\cite{Liu.ea2015:AnnexinA2complexeswith,Hutchinson.ea2011:Molecularregulatorsofresolution,Aarli.ea1997:Suppressiveeffectonlymphoproliferation}.
We suggest that further research into molecular role of these annexin
complexes may illuminate how immune tolerance is maintained during
placentation. The core placenta transcriptome is also enriched in
genes involved in maintaining the structure of the placenta and
transporting proteins, as would be expected given the function of the
placenta.

@@

The core placenta transcriptome was also identified, which contains
genes which are involved in maternal-fetal tolerance, such as the
annexins, and genes responsible for cell-cell and cell-matrix
interactions, such as \textit{LGALS1}. These genes were almost
certainly present in the placenta of the common mammalian ancestor. We
hypothesize that modifications to their expression or function will
compromise the development and organization of the placenta.
